---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%",
  dpi = 300
)
```

# ggoce

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![R-CMD-check](https://github.com/paleolimbot/ggoce/workflows/R-CMD-check/badge.svg)](https://github.com/paleolimbot/ggoce/actions)
[![Codecov test coverage](https://codecov.io/gh/paleolimbot/ggoce/branch/master/graph/badge.svg)](https://codecov.io/gh/paleolimbot/ggoce?branch=master)
<!-- badges: end -->

The goal of ggoce is to provide a minimal set of [ggplot2](https://ggplot2.tidyverse.org) components to make publication-quality plots of [oce](https://dankelley.github.io/oce/) objects. **It is currently under initial proof-of-concept development and should be used for entertainment purposes only.**

## Installation

You can install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("remotes")
remotes::install_github("paleolimbot/ggoce")
```
## Example

This is a basic example which shows you how to solve a common problem:

```{r example, message=FALSE, warning=FALSE}
library(ggplot2)
library(ggoce)
theme_set(theme_oce())
data(ctd, package = "oce")

ggplot(ctd, aes(x = salinity, y = depth)) +
  geom_point() +
  scale_y_reverse()
```

```{r example-sec}
data(section, package = "oce")

ggplot(section, aes(distance, pressure)) +
  geom_point(aes(col = temperature)) +
  scale_y_reverse() +
  scale_colour_viridis_b()
```
