---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%",
  dpi = 300
)
```

# ggoce

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![R-CMD-check](https://github.com/paleolimbot/ggoce/workflows/R-CMD-check/badge.svg)](https://github.com/paleolimbot/ggoce/actions)
[![Codecov test coverage](https://codecov.io/gh/paleolimbot/ggoce/branch/master/graph/badge.svg)](https://codecov.io/gh/paleolimbot/ggoce?branch=master)
<!-- badges: end -->

The goal of ggoce is to provide a minimal set of [ggplot2](https://ggplot2.tidyverse.org) components to make publication-quality plots of [oce](https://dankelley.github.io/oce/) objects. **It is currently under initial proof-of-concept development and should be used for entertainment purposes only.**

## Installation

You can install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("remotes")
remotes::install_github("paleolimbot/ggoce")
```
## Example

The ggoce package lets you pass 'oce' objects into ggplot2 functions as if they were data frames.

```{r example, message=FALSE, warning=FALSE}
library(ggplot2)
library(ggoce)
theme_set(theme_oce())
data(ctd, package = "oce")

ggplot(ctd, aes(x = salinity, y = depth)) +
  geom_point() +
  scale_y_reverse()
```

You can see the actual data frames that are generated by calling the `fortify()` methods directly. The `fortify()` methods are defined are for "ctd", "section", and "adp" objects.

```{r}
data(ctd, package = "oce")
data(section, package = "oce")
data(adp, package = "oce")


fortify(ctd)
fortify(section)
fortify(adp)
```

For "section" and "adp" objects, there is more than one data frame one might want to plot. To obtain these tables, call `fortify()` directly and use the `which` argument:

```{r}
fortify(section, which = "metadata")
fortify(section, which = "data")
fortify(section, which = "combined")

fortify(adp, which = "metadata")
fortify(adp, which = "bottom_track")
fortify(adp, which = "velocity")
```

The default methods for each of these are called when you pass it to `ggplot()` and are chosen such that the variables you probably want to use are available:

```{r example-sec}
ggplot(section, aes(distance, pressure)) +
  geom_point(aes(col = temperature)) +
  scale_y_reverse() +
  scale_colour_viridis_b()
```

```{r example-adp}
ggplot(adp, aes(time, distance, fill = v)) +
  geom_raster() +
  facet_grid(vars(beam)) +
  scale_fill_gradient2(limits = function(x) c(-max(abs(x)), max(abs(x)))) +
  coord_cartesian(expand = FALSE)
```

## TS plots

The ggoce package provides `geom_isopycnal()` to support creating standard temperture/salinity diagrams.

```{r example-ts}
ggplot(
  ctd,
  aes(
    x = salinity,
    y = oce::swTheta(
      salinity,
      temperature,
      pressure
    )
  )
) +
  geom_isopycnal() +
  geom_point() +
  labs(
    x = "Practical salinity",
    y = "Potential Temperature (°C)"
  )
```
